---
title: "Fig1b"
author: "Your Name"
date: "2023-03-12"
output: workflowr::wflow_html
editor_options:
  chunk_output_type: console
---

## Introduction

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE,cache = FALSE,warning = FALSE,message = FALSE,fig.path = "./Figs/")

```


```{r,echo=F,message=FALSE}
library("dplyr")
library("tidyverse")
library("survival")
library("survminer")
library("eulerr")
library("ggplot2")
library("reshape")
library("ggfortify")
library("gridExtra")
library("survMisc")
library("rsq")
library("pROC")
library("data.table")
library("RColorBrewer")
library("gt")
library("DT")
library(plotly)
library(dplyr)
library(carData)
library(gapminder)
library(babynames)
col_pce <- rev(brewer.pal(10, "Paired"))
col_p = c(col_pce[1:3],
          col_pce[5],
          col_pce[4],
          col_pce[c(6, 10)],
          "black",
          col_pce[9],
          "turquoise",
          col_pce[7])
tems = theme(
  axis.text.x = element_text(
    color = "grey20",
    size = 20,
    angle = 90,
    hjust = .5,
    vjust = .5,
    face = "plain"
  ),
  axis.text.y = element_text(
    color = "grey20",
    size = 20,
    angle = 0,
    hjust = 1,
    vjust = 0,
    face = "plain"
  ),
  axis.title.x = element_text(
    color = "grey20",
    size = 20,
    angle = 0,
    hjust = .5,
    vjust = 0,
    face = "plain"
  ),
  axis.title.y = element_text(
    color = "grey20",
    size = 20,
    angle = 90,
    hjust = .5,
    vjust = .5,
    face = "plain"
  )
)

```



## FHS

```{r framingham}
### plot with PVE
fig_path="./Figs/Fig1b/"
f3=readRDS("output/fh_PRS.rds")
df=readRDS("output/fh_full.rds")


dat=data.frame(df %>%group_by(round(AGE1,0)) %>%summarise(length(AGE1)))
dat=dat[c(11:50),]

hazards=matrix(data=NA,nrow=nrow(dat),ncol=27)
errors=matrix(data=NA,nrow=nrow(dat),ncol=7)
library("survival")
df$round_age=round(df$AGE1,0)
df$ldl.quant=scale(df$CALC_LDL1)
df$sbp.quant=scale(df$SBP1)
df$hdl.quant=scale(df$HDL1)
df$chol.quant=scale(df$TC1)
df$bmi.quant=scale(df$BMI1)
df$sex=ifelse(df$SEX==1,1,0)
df$chd.years=df$chddate/365.2+df$AGE1
f3$round_age=round(f3$AGE1,0)
f3$chd.years=f3$chddate/365.2+f3$AGE1
f3$prs.quant=scale(f3$V2)
f3$sex=ifelse(f3$SEX==1,1,0) ## in framingham 2 is female, 1 is male

#hazards=readRDS("output/hazards_.rds")
hazards=data.frame(readRDS("output/hazards_fhs_EQ.rds"))
hazards=data.frame(hazards)

hazards=data.frame(hazards)
colnames(hazards)=c("prs.HR","prs.OR","prs.r2",
                    
                    "ldl.HR","ldl.OR","ldl.r2",
                    
                    "smoke.HR","smoke.OR","smoke.r2",
                    "age.HR","age.OR","age.r2",
                    "sbp.HR","sbp.OR","sbp.r2",
                    #"dm.HR","dm.OR","dm.r2",
                    "chol.HR","chol.OR","chol.r2",
                    "bmi.HR","bmi.OR","bmi.r2",
                    "sex.HR","sex.OR","sex.r2",
                    
                    "hdl.HR","hdl.OR","hdl.r2")




hrmat=hazards[,grep("HR",colnames(hazards))];hrmat$age=dat$round.AGE1..0.

ormat=hazards[,grep("OR",colnames(hazards))];ormat$age=dat$round.AGE1..0.
r2mat=hazards[,grep("r2",colnames(hazards))];r2mat$age=dat$round.AGE1..0.

colnames(hrmat)=colnames(ormat)=colnames(r2mat)=c("Polygenic Score","LDL Cholesterol","Smoking","Age","Systolic blood pressure","Total cholesterol","Body Mass Index","Male Sex","High-density Lipoprotein","age")

#####
```


````{r new}

upperbound=data.frame(readRDS("output/hazards_rate_upperbound_fh_EQ.rds"))
lowerbound=data.frame(readRDS("output/hazards_rate_lowerbound_fh_EQ.rds"))


upperbound$age=dat$round.AGE1..0.
u=melt(upperbound,id.vars="age")

lowerbound$age=dat$round.AGE1..0.
l=melt(lowerbound,id.vars="age")


##### Bring together
haz=melt(hrmat,id.vars = "age")
ors=melt(ormat,id.vars = "age")
r2s=melt(r2mat,id.vars = "age")

haz$low.se = l$value
haz$upper.se = u$value


s=reshape(haz, direction = "wide",
idvar = "age", timevar = "variable")
write.csv(s,"output/hrindex_fhs_eq.csv",row.names = F)
```

```{r}

r2s$variable=ors$variable=haz$variable <- factor(haz$variable, levels = c("Total cholesterol","Male Sex","Smoking","Polygenic Score","LDL Cholesterol","Systolic blood pressure","Body Mass Index","Age","High-density Lipoprotein"))

hr_fhs = ggplot(subset(
  haz,
  variable %in% c(
    "Polygenic Score",
    "Total cholesterol",
    "Systolic blood pressure",
    "Pooled cohort equations",
    #"Age",
    "Smoking",
    "Male Sex",
    "High-density Lipoprotein",
    "Smoking")), aes(age, value, colour = variable,fill=variable)) +
  #geom_point(size = 1) + 
  stat_smooth(method = "loess") + labs(y = "Hazard Ratio of Coronary Artery Disease", x ="Age of Risk Assessment", colour = "Risk Factor") + scale_color_manual(values = col_p,drop = TRUE,breaks = c("Diabetes mellitus","Male Sex","Smoking","Polygenic Score","LDL Cholesterol","Systolic blood pressure",
"Body Mass Index","Pooled cohort equations","Age","High-density Lipoprotein",
"Total cholesterol"),guide="none")+
  scale_fill_manual(values=col_p, drop=TRUE, breaks=c("Diabetes mellitus","Male Sex","Smoking","Polygenic Score","LDL Cholesterol","Systolic blood pressure","Body Mass Index","Pooled cohort equations","Age","High-density Lipoprotein","Total cholesterol"),guide="none")


r2_fhs = ggplot(subset(
  r2s,
  variable %in% c(
    "Polygenic Score",
    "Total cholesterol",
    "Systolic blood pressure",
    "Pooled cohort equations",
    #"Age",
    "Smoking",
    "Male Sex",
    "High-density Lipoprotein",
    "Smoking")
), aes(age, value, colour = variable,fill=variable))+
  #geom_point(size = 1) +
  stat_smooth(method = "loess") + labs(y = "Proportion of Variation Explained", x ="Age of Risk Assessment", colour = "Risk Factor") + scale_color_manual(values = col_p,drop = TRUE,breaks = c("Diabetes mellitus","Male Sex","Smoking","Polygenic Score","LDL Cholesterol","Systolic blood pressure","Body Mass Index","Pooled cohort equations","Age","High-density Lipoprotein","Total cholesterol"))+
  scale_fill_manual(values=col_p, drop=TRUE, breaks=c("Diabetes mellitus","Male Sex","Smoking","Polygenic Score","LDL Cholesterol","Systolic blood pressure","Body Mass Index","Pooled cohort equations","Age","High-density Lipoprotein","Total cholesterol"),guide="none")

h1=hr_fhs+theme_classic(base_size = 20)+tems
# 
# ggsave(h1,file="hr_fhs_nob.tiff",dpi = 300,width = 6,height = 6)

r2=r2_fhs+theme_classic(base_size = 20)+theme(legend.position = "none")+tems
saveRDS(r2,"output/r2fhs.rds")
h1=h1+theme_classic(base_size = 20)+theme(legend.position = "none")+tems
saveRDS(h1,"output/h1hs_noeq.rds")

ggsave(h1,file=paste0(fig_path,"hr_fhs.tiff"),dpi = 300,width = 6,height = 6)
ggsave(r2,file=paste0(fig_path,"r2_fhs.tiff"),dpi = 300,width = 6,height = 6.1)
```

```{r}
ggplotly(h1)
```


```{r}
ggplotly(r2)
```


# Hazard Rate Lookup Table
```{r}
library(DT)
m=cbind(haz[,c(1:2)],round(haz[,c(3:5)],2))
colnames(m)=colnames(haz)
DT::datatable(m)
```

# Proportion Variation Explained Lookup Table
```{r}
library(DT)
m=cbind(r2s[,c(1:2)],round(r2s[,c(3)],2))
colnames(m)=colnames(r2s)
DT::datatable(m)
```

# Merge files for joint panel

```{r}
hall=readRDS("output/hall.rds")
r2u=readRDS("output/r2.rds")
h1=readRDS("output/h1hs.rds")
r2fhs=readRDS("output/r2fhs.rds")
r2_fhs=r2fhs+ggtitle("FHS")+theme_classic(base_size=15)+labs(x="Age of Risk Assessment, years")+theme(legend.text = element_text(size = 15), legend.title = element_text(size = 15), axis.text.x = element_text(size = 15),axis.text.y = element_text(size = 15))

r2u=r2u+ggtitle("UKB")+theme_classic(base_size=15)+labs(x="Age of Risk Assessment, years")+theme(legend.text = element_text(size = 15), legend.title = element_text(size = 15), axis.text.x = element_text(size = 15),axis.text.y = element_text(size = 15))

h1=h1+ggtitle("FHS")+theme_classic(base_size=15)+ylim(0,5)+labs(x="Age of Risk Assessment, years")+theme(legend.text = element_text(size = 15), legend.title = element_text(size = 15), axis.text.x = element_text(size = 15),axis.text.y = element_text(size = 15))

hall = hall + ggtitle("UKB") + theme_classic(base_size=15) + ylim(0,5) + labs(x="Age of Risk Assessment, years") + theme(legend.text = element_text(size = 15), legend.title = element_text(size = 15), axis.text.x = element_text(size = 15),axis.text.y = element_text(size = 15))


print1=ggarrange(h1,hall, ncol=2, common.legend = TRUE, legend="bottom",labels = c("A.","B."),heights=c(3.5,3.5))

print2=ggarrange(r2_fhs,r2u, ncol=2, common.legend = TRUE, legend="bottom",labels = c("A.","B."))


ggsave(print1,filename = "Figs/Fig1combined_noeq.tiff",dpi = 300,width = 10,height=6)

ggsave(print2,filename = "Figs/Fig2combined.tiff",dpi = 300,width = 10,height=6)
