---
title: "Fig5"
author: "Sarah Urbut"
date: "2023-03-12"
output: workflowr::wflow_html
editor_options:
  chunk_output_type: console
---
  
## Introduction


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE,cache = FALSE,warning = FALSE,message = FALSE,fig.path = "./Figs/",message = FALSE,warning = FALSE)

```

## AUC overall

```{r}
source("code/utils.R")
library(ggplot2)

df=readRDS("output/amit_df.rds")

ages=c(40,45,50,55,60,65,70,75)
df$age.cat=cut(df$phenos.enrollment,breaks = c(40,45,50,55,60,65,70,75))
thresh=seq(0.5,1,by=0.01)
true.pos.p=matrix(NA,nrow=length(levels(df$age.cat)),ncol=length(thresh))
false.pos.p=matrix(NA,nrow=length(levels(df$age.cat)),ncol=length(thresh))

for(a in 1:length(levels(df$age.cat))){
  #print(a)
for(i in 1:length(thresh)){
  t=thresh[i]
  age=levels(df$age.cat)[a]
  case=intersect(which(df$phenos.has_CAD==1),which(df$age.cat==age))
  control=intersect(which(df$phenos.has_CAD==0),which(df$age.cat==age))
  true.pos.p[a,i]=mean(df[case,prs.r>t])
  false.pos.p[a,i]=mean(na.omit(df[control,prs.r>t]))
}}

par(mfrow=c(3,3))
for(i in 1:length(levels(df$age.cat))){
  plot(false.pos.p[i,],true.pos.p[1,],pch=19,col=i,xlab="False Positive Rate",ylab="True Positive Rate",main=paste0("PRS:",df$age.cat[i]))
  }

true.pos.a=matrix(NA,nrow=length(levels(df$age.cat)),ncol=length(thresh))
false.pos.a=matrix(NA,nrow=length(levels(df$age.cat)),ncol=length(thresh))

thresh=seq(5,25,by=1)
for(a in 1:length(levels(df$age.cat))){
  #print(a)
for(i in 1:length(thresh)){
  t=thresh[i]
  age=levels(df$age.cat)[a]
  case=intersect(which(df$phenos.has_CAD==1),which(df$age.cat==age))
  control=intersect(which(df$phenos.has_CAD==0),which(df$age.cat==age))
  true.pos.a[a,i]=mean(df[case,ascvd_10y_accaha_all>t])
  false.pos.a[a,i]=mean(na.omit(df[control,ascvd_10y_accaha_all>t]))
}}

  true.pos.a=sum(df$asc>i[df$phenos.has_CAD==1&df$phenos.age.cat==a])
  false.pos.p=sum(df$prs.r>i[df$phenos.has_CAD==0&df$phenos.age.cat==a])
  
par(mfrow=c(3,3))
for(i in 1:length(levels(df$age.cat))){
  plot(false.pos.a[i,],true.pos.a[1,],pch=19,col=i,xlab="False Positive Rate",ylab="True Positive Rate",main=paste0("ASCVD:",df$age.cat[i]))
  }
``
